---
title: "S3 Cross Account Access"
author: "Jerome Dixon"
date: "1/12/2022"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)


library(here)
library(here)
library(aws.s3)
library(aws.signature)

```

# Setup AWS credentials according to this:
https://www.gormanalysis.com/blog/connecting-to-aws-s3-with-r/
https://support.rstudio.com/hc/en-us/articles/360047157094-Managing-R-with-Rprofile-Renviron-Rprofile-site-Renviron-site-rsession-conf-and-repos-conf

# Key comment: The usethis package includes a helper function for editing .Renviron files from an R session with usethis::edit_r_environ(). 

# Cross Account Access for S3 Bucket
Cross Account Bucket- arn:aws:s3:::{bucket-name}
Cross Account User - "AWS": "arn:aws:iam::123456789012:user/user_name"

# Direct Account Access
1. Create organizational account with S3 programmatic access only. Save credentials 

2. via AWS CLI/shell command create profile with credentials: aws configure --profile {profile_name}

# Configure Multiple Accounts
# Account1
aws configure --profile account1
AWS_ACCESS_KEY_ID={AWS_ACCESS_KEY_ID_ACCOUNT1}
AWS_SECRET_ACCESS_KEY_ID={AWS_SECRET_ACCESS_KEY_ID1}
AWS_DEFAULT_REGION=us-east-1

# Account2
aws configure --profile account2
AWS_ACCESS_KEY_ID={AWS_ACCESS_KEY_ID_ACCOUNT2}
AWS_SECRET_ACCESS_KEY={AWS_SECRET_ACCESS_KEY_ID2}
AWS_DEFAULT_REGION=us-east-1

3. Switch between profiles as needed (aws.signature)
use_credentials(profile = "account2")



```{sh S3-Bucket-Access}

aws s3api put-bucket-policy --bucket {bucket_name} --policy file://s3-access-bucket.json --profile {profile_name}


```


```{sh User-Access-Policy}

aws iam create-policy --policy-name s3-access --policy-document file://s3-access-user.json --profile default

```


```{r}

use_credentials(profile = "default")

```


#Attach to user in IAM console - Doesn't work very well
```{sh Attach-Policy-User}

aws iam attach-user-policy --policy-arn arn:aws:iam::123456789:policy/s3-access --user-name {user_name}

```


# Preferred Method
```{r test-s3}

use_credentials(profile = "default")

get_bucket(bucket = "{bucket_name}")

```
